Work Fragmentation in Developer Interaction Data

### 2016-07-04 paper_2.tex
Reviews 1.2, 1.3 and 1.5

An important reason to consider the edit ratio is that having an interruption requires doing activities that might increase the execution of selection events, reducing the edit events. For example reading the code, navigating around files and starting a debugging sessions are activities heavily loaded with selections events and are common activities after an interruption, according to observational studies. The edit ratio can tell us when there is a reduction of edit events due to (mainly) selection events.

@@

We did a correlation analysis (using Pearson's correlation coefficient) involving these three metrics (Table \ref{tbl:corr_analysis}, classifying the data between traces with or without interruptions. We found that the Edits/min and Selections/minute metrics have a degree of correlation, but that it is relatively low, this is the expected result as they explain two different kind of activities. We do find that the correlation is higher in traces with interruptions. The same happens between the Selections/minute and Edit ratio metrics with the data of both kind of traces, this time being a negative correlation which is also an expected value, as the Edit ratio should decrease when the Selections/minute increases.

The Edit/minute and Edit ratio correlation coefficient is higher in both groups, but not high enough to discard the latter, for it tells something different from the user activity. It is normal to see these two metrics with a moderate correlation coefficient given that the Edit ratio is the proportion of edition events over all events in a minute.

@@

Beyond visual inspection, we also quantify the statistical and the practical significance of these observations. First, in the results with Mylyn, all the differences observed are statistically significant with very low p-values (see Table~\ref{tbl:p_value}) according to the Mann-Whitney U-test. This is not surprising, given the shape of the boxplots and the size of the samples.

>>>>

An important reason to consider the edit ratio is that having an interruption requires doing activities that might increase the execution of selection events, reducing the edit events. For example reading the code, navigating around files and starting a debugging sessions are activities heavily loaded with selections events and are common activities after an interruption, according to observational studies \cite{PR11}. The edit ratio can tell us when there is a reduction of edit events due to (mainly) selection events.

@@

We did a correlation analysis (using Pearson's correlation coefficient) involving these three metrics (Table \ref{tbl:corr_analysis}, classifying the data between traces with or without interruptions. We found that the Edits/min and Selections/minute metrics have a degree of correlation ($r=0.25$ and $r=0.35$), but that it is relatively low; this is the expected result as they explain two different kinds of activities. We do find that the correlation is higher in traces with interruptions. The same happens between the Selections/minute and Edit ratio metrics with the data of both kind of traces ($r=-0.38$ and $r=-0.32$), this time being a negative correlation which is also an expected value, as the Edit ratio should decrease when the Selections/minute increases.

The Edit/minute and Edit ratio correlation coefficient is higher in both groups ($r=0.65$ and $r=0.60$), but not high enough to discard the latter, for it tells something different from the user activity. It is normal to see these two metrics with a moderate correlation coefficient given that the Edit ratio is the proportion of edition events over all events in a minute.

@@

Beyond visual inspection, we also quantify the statistical and the practical significance of these observations. First, in the results with Mylyn, all the differences observed are statistically significant with very low p-values (see Table~\ref{tbl:p_value}) according to the Mann-Whitney U-test. This is not surprising, given the shape of the boxplots and the size of the samples. It is important to mention that the values from the effect size Tables (\ref{tbl:p_value} and \ref{tbl:p_value_udc}) are obtained by comparing the \textit{none} group with the rest of the groups.
